Synpotic Soil Characterization

### 2025-02-21 3-reports/manuscript_figures.Rmd
update file path

elevation = read.csv("synoptic-distances.csv", na = "")
elevation_processed = 
  elevation %>% 
  mutate(transect = factor(transect, levels = c("water edge", "wetland", "transition", "upland"))) %>% 
  reorder_site()

>>>>

elevation = read.csv("1-data/synoptic-elevations.csv", na = "")
elevation_processed = 
  elevation %>% 
  mutate(transect = factor(transect, levels = c("water edge", "wetland", "transition", "upland"))) %>% 
  reorder_site()
